\Large Bayes network classifiers for fMRI

### 2012-09-14 proposal/proposal.tex
minor changes

\begin{description}
	\item[11th - 21st September]\-\\
	During this time period, the group members will conduct an initial research. The research will focus on the Bayes network classifiers and especially on the TAN tree algorithm.
	\item[22nd - 28th September]\-\\
	During this time period, the definition of the various models will be realised.
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation ...
	\item[20th - 22nd October]\-\\
	During this time period the group members will prepare the presentation of the project.
	\item[28th October]\-\\
	Until the aforementioned date the final version of the document and the implementation will be delivered.
\end{description}

>>>>

\begin{description}
	\item[11th - 21st September]\-\\
	During this time period, the group members will conduct an initial research. The research will focus on the Bayes network classifiers and especially on the TAN tree algorithm.
	\item[22nd - 28th September]\-\\
	During this time period, the definition of the various models will be realised.
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation.
	\item[20th - 22nd October]\-\\
	During this time period the group members will prepare the presentation of the project.
	\item[28th October]\-\\
	Until this date the final version of the document and the implementation will be delivered.
\end{description}
